The imprint of global magma oceans on exoplanet demographics

### 2023-01-21 src/tex/ms.tex
discuss sensitivity of detectability on x_H2O and f_rgh

\begin{note}
    Given an optimistic survey design, what influences the probability of correctly rejecting a false null hypothesis?
    \begin{figure}[ht!]
%    \script{figurescript.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/optimistic_statpwr_H2O-f.pdf}
            \caption{
                Statistical power of the runaway greenhouse hypothesis test as a function of model parameters.
                For a sample size $N = \Nplanets$, the color code shows the fraction of simulations resulting in a sound detection ($\Delta \ln \mathcal{Z} > 3$) for different combinations of water mass fraction and fraction of greenhouse climate planets.
                Higher values in either parameter result in a more reliable detection.
            }
            \label{fig:statpwr_H2O-f}
        \end{centering}
    \end{figure}
    Figure~\ref{fig:statpwr_H2O-f} explores the statistical power achieved in the above scenario for different combinations of the poorly constrained parameters $x_{H_2O}$ and $f_\mathrm{rgh}$.
    The higher the water content and thus the radius change, and the higher the fraction of planets in runaway greenhouse climates, the greater the prospect of a statistically sound detection.
    As long as this fraction is larger than $\sim 0.1$, a sample size of \Nplanets\ is sufficient for a $\SI{50}{\percent}$ detection rate even for water ratios as low as $x_{H_2O} = 0.001$.
\end{note}

>>>>

\begin{note}
    Given an optimistic survey design, what influences the probability of correctly rejecting a false null hypothesis?
    \begin{figure}[ht!]
%    \script{figurescript.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/optimistic_statpwr_H2O-f.pdf}
            \caption{
                Statistical power of the runaway greenhouse hypothesis test as a function of model parameters.
                For a sample size $N = \Nplanets$, the color code shows the fraction of simulations resulting in a sound detection ($\Delta \ln \mathcal{Z} > 3$) for different combinations of water mass fraction and fraction of greenhouse climate planets.
                Higher values in either parameter result in a more reliable detection.
            }
            \label{fig:statpwr_H2O-f}
        \end{centering}
    \end{figure}
    Figure~\ref{fig:statpwr_H2O-f} explores the statistical power achieved in the above scenario for different combinations of the poorly constrained parameters $x_{H_2O}$ and $f_\mathrm{rgh}$.
    The higher the water content and thus the radius change, and the higher the fraction of planets in runaway greenhouse climates, the greater the prospect of a statistically sound detection.
     $f_\mathrm{rgh}$ dominates this trend: It enters linearly into the average planet radius, whereas the contribution of $x_{H_2O}$ - as predicted by the geophysical models - is sublinear with a power-law exponent of $\sim 0.3$.
    As long as $f_\mathrm{rgh}$ is larger than $\sim 0.1$, a sample size of \Nplanets\ is sufficient for a $\SI{50}{\percent}$ detection rate even for water ratios as low as $x_{H_2O} = 0.001$.
\end{note}
